\section{Exporting RPNA data from WRDS}

The RavenPack News Analytics dataset is split by year and by product in the WRDS database. Hence, the source table in the code below (DJ\_EQUITIES\_2000) needs to be changed for each year, and EQUITIES needs to be replaced by GLOBAL\_MACRO for non-equity stories. This amounts to a total of 40 tables to then export in CSV format.

\begin{listing}[ht]
\inputminted[frame=lines, linenos]{sas}{code/RPNA_export.txt}
\caption{SQL procedure run in SAS Studio to export RPNA tables from WRDS Cloud}
\label{snippet:RPNA}
\end{listing}

% ---------------------------------------------
\section{Tables Schema}

Decide whether to include all columns or only the ones that were actually used. Also, is it better to provide a table or the code used to create the tables? And, to what extent should I describe the process from of import from CSV to SQL Server tables? To what extent should I describe the columns that I don't use (I already reference the official CRSP documentation)?\todo{I would not describe what I did not use as it produces tables that don't fit on a page.} RPNA documentation is only available to clients. \todo{Clarify this before doing more work.}

%\input{tables/test_table}

%----------------------------------------------
\begin{landscape}

\section{Trade and Quote Data}
\label{appx:taq}

Table \ref{table:appx_taq_corr} is reproduced from page 19 of the TAQ 3 User's Guide (\cite{TAQUserGuide}).

\begin{table}
\centering

\begin{tabular}{l|c|l|}
    \cline{2-3}
	 & Code & Description \\
    \hline
    \multirow{3}{*}{Good Trades} & 0 & Regular trade that was not corrected, changed, or signified as cancel or error \\
     							 & 1 & Original trade which was later corrected. This record contains the original time and the corrected data for the trade \\
                                 & 2 & Symbol correction (out of time sequence) \\
    \hline
	\multirow{3}{*}{Original trade records} & 7 & Trade cancelled due to error \\
     							            & 8 & \textbullet Trade cancelled \\
                                            & 9 & Trade cancelled due to symbol correction \\
    \hline
    \multirow{3}{*}{Correction instructions} & 10 & Cancel record (associated with 8) \\
     							             & 11 & Error record (associated with 7) \\
                                             & 12 & Correction record (associated with 1; contains corrected time and original data) \\
    \hline
\end{tabular}

\caption{Correction Indicator. TAQ shows only the original trade and final correction. No interim corrections are shown.}
\label{table:appx_taq_corr}
\end{table}

\end{landscape}